A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-06 manuscript.Rmd
cite another reference for copyright

Note that publishing data, code, or other materials is not sufficient to allow other users to use it, modify it, or redistribute it. For example, according to German copyright law, a repository without a license must be assumed to be protected by copyright <!-- AP citation needed -->. In many countries (i.e. the USA, European Union), a content creator has exclusive right to use their creation.
A license is the legal authorization of other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media (such as stimulus materials if you created them).
In contrast, scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com).
However, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after adding a license, they give their consent by contributing.
To add a CC-BY license to your project, simply run (there are similar commands for other licenses):

>>>>

Note that publishing data, code, or other materials is not sufficient to allow other users to use it, modify it, or redistribute it. For example, according to German copyright law, a repository without a license must be assumed to be protected by copyright ([UrhG[^urhg]](https://www.gesetze-im-internet.de/englisch_urhg/englisch_urhg.html), Section 1, 7, 11). In many countries (i.e. the USA, European Union), a content creator has exclusive right to use their creation[@stoddenLegalFrameworkReproducible2009].
A license is the legal authorization of other people to use what you have created.
<!---exact copy from our previous manuscript, do we need to change? -->
In our experience, the [Creative Commons - Attribution license (CC-BY)](https://creativecommons.org/licenses/by/4.0/) is often appropriate for sharing texts, R Markdown files, generated figures, and other media (such as stimulus materials if you created them).
In contrast, scripts and any other computer code are often best shared under the [MIT license](https://opensource.org/licenses/MIT) (or similar permissive licenses).
Copyright does often not apply to data, we therefore recommend to share data with a CC0 license to clarify that you do not hold copyright to it.
Giving data another license than CC0 is often just confusing, because a license is invalid if there is no copyright.
All licenses assure maximal freedom for future users while requiring the attribution, if possible, of the original authors in derivative work.
These licenses are also in line with the recommendations by the Reproducible Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
A great resource to choose a license is [choosealicense.com](https://choosealicense.com).
However, no resource, including our recommendation, replaces legal advice.
<!-- plagiary end -->
It is important to get written consent from collaborators when you change/add the license.
However, if their first contribution occurs after adding a license, they give their consent by contributing.
To add a CC-BY license to your project, simply run (there are similar commands for other licenses):
